NLO QCD+EW corrections to diphoton production in association with a vector boson

### 2017-10-25 results.tex
small overhaul of aaa results section

\begin{figure}[t!]
  \centering
  \includegraphics[width=0.32\textwidth]{figs_aaa/pT_y1}
  \includegraphics[width=0.32\textwidth]{figs_aaa/pT_y2}
  \includegraphics[width=0.32\textwidth]{figs_aaa/pT_y3}
  \caption{
    Transverse momentum of the leading (left), subleading (centre) 
    and third leading (right) photon 
    in triple photon production at the LHC at 13\,TeV. 
    The distributions are shown at LO (blue), NLO QCD (green), 
    NLO EW (orange), NLO \QCDpEW\ (red) and NLO \QCDtEW\ (black) 
    including scale uncertainties. The top ratio plot details 
    the relative corrections to the leading order cross section 
    without applying any jet veto, while the centre ratio plot 
    applies a jet veto of $p_\mathrm{T,jet}^\mathrm{veto}=\text{30\,GeV}$. 
    The lower ratio highlights the size of the electroweak corrections.
    \label{fig:aaa:pt}
  }
\end{figure}

Figure \ref{fig:aaa:pt} displays the transverse momenta of the 
first three leading photons. 
The NLO QCD corrections exhibit a handful of interesting features. 
Firstly, in the absence of a jet veto the fixed-order calculation 
exhibits a huge correction factors, mainly induced by the 
opening of new channels in the real emission. 
Similar, kinematic constraints present at LO \footnote{
  At leading order the leading photon needs to be in a different 
  hemisphere than both the subleading and third leading photon. 
  Thus, $\Delta\phi_{\gamma_1\gamma_2}$ and $\Delta\phi_{\gamma_1\gamma_3}$ 
  must be larger that $\tfrac{1}{2}\,\pi$.
} are released and 
lead to a larger phase space that can be populated. 
These findings mandate the inclusion of at least the $\aaa+\text{jet}$ 
production process at NLO QCD to arrive at a reliable description 
of inclusive \aaa\ production, and thus either a NNLO QCD calculation 
or a multijet merging ansatz \cite{Hoeche:2012yf,Kallweit:2015dum}. 
While the inclusive QCD corrections at very small transverse momenta 
are universally large for all three leading photon \pT-spectra 
($\deltaQCD\approx 2$), they remain at exorbitantly large 
($\deltaQCD\approx 1.5$) throughout the considered range 
only for the leading jet \pT. 
For both subleading photons the QCD corrections are quickly 
decreasing, leveling out at a $\approx 20\%$ at large transverse 
momenta.
In the presence of a restrictive jet veto the very low transverse 
momentum region still experiences large correction of about 
$\deltaQCD\approx 1$. 
As transverse momenta are increasing, the QCD corrections now turn 
negative reaching now $-50-60\%$ and for all three photons.

The electroweak corrections, due to the absence of the opening 
of large new channels at the next-to-leading order, are dominated 
by the virtual corrections. 
Consequently, the phase space restrictions present at leading 
order are still respected.
For all three photons they are small but positive at small 
transverse momenta and exhibit the usual Sudakov shape at 
large transverse momenta.
They reach $-10\%$ for the leading and subleading photon and 
$-20\%$ for the third photon at $\pT=500\,\text{GeV}$. 
Due to the different sizes of the QCD and electroweak 
corrections, the additive and multiplicative combination 
of corrections lead to very similar results.

@@

Figure \ref{fig:aaa:myy} continues with the three diphoton 
invariant masses. 
The \pT\ and $\Delta R$ requirements 
of the event selection induce a minimum in the distributions 
at leading order. 
The region below can only be filled if a fourth particle is 
present, as is the case in both the QCD and electroweak real 
emission corrections, leading to simultaneously huge 
corrections \deltaQCD\ and \deltaEW\ as the Born cross 
section vanishes. 
Due to this behaviour, the multiplicative combination of 
corrections, NLO \QCDtEW, ceases to be well defined and 
spikes in the distribution are visible.
The distributions below, where $\rd\sigma_\text{LO}=0$, 
are ill-defined. 
In consequence, for distributions where kinematic boundaries 
exist at leading order, but are lifted at higher orders, 
the multiplicative combination does not present a viable 
option for a good description of the observable 
throughout phase space.

The QCD corrections themselves again exceed $200\%$ at 
small invariant masses, already well before the above 
described kinematic boundary effect takes hold. 
As the invariant masses are increasing, the 
QCD corrections are dropping to $20-30\%$ for the inclusive 
selection. 
The structure the QCD corrections exhibit around 80-90\,GeV 
in all three diphoton-pair invariant masses are induced by 
the acceptance cuts.
In the presence of the jet veto, the QCD corrections are 
reduced and turn negative beyond $m_{\gamma\gamma}\gtrsim 300\,\text{GeV}$ 
reaching around $-40\%$ at 1\,TeV. 
The electroweak corrections, on the other hand, are 
again moderate, ranging from $+1.5\%$ between 70 and 200\,GeV 
for $m_{\gamma_1\gamma_2}$ and $m_{\gamma_1\gamma_2}$ and 
0 and 100\,GeV for $m_{\gamma_2\gamma_3}$. 
$m_{\gamma_1\gamma_2}$ exhibits a small rise in the correction 
at $2m_W$ due to resonant box diagrams in that region. 
This feature is also present in the electroweak corrections 
to diphoton production in this observable \cite{Chiesa:2017gqx}. 
At large transverse momentum the usual Sudakov logarithms 
are recoveren, resulting in corrections of around 
$-8\%$ at 1\,TeV for all photon-pair invariant masses.

@@

\begin{itemize}
  \item \pT of 3rd photon much softer than 1st and 2nd
  \item in all cases NLO EW outside LO uncertainty band
\end{itemize}

@@

\comment{MS: is that $\ell^+$ or $\ell^-$?}

>>>>

\begin{figure}[t!]
  \centering
  \includegraphics[width=0.32\textwidth]{figs_aaa/pT_y1}
  \includegraphics[width=0.32\textwidth]{figs_aaa/pT_y2}
  \includegraphics[width=0.32\textwidth]{figs_aaa/pT_y3}
  \caption{
    Transverse momentum of the leading (left), subleading (centre) 
    and third leading (right) photon 
    in triple photon production at the LHC at 13\,TeV. 
    The distributions are shown at LO (blue), NLO QCD (green), 
    NLO EW (orange), NLO \QCDpEW\ (black) and NLO \QCDtEW\ (red) 
    including scale uncertainties. The top ratio plot details 
    the relative corrections to the leading order cross section 
    without applying any jet veto, while the centre ratio plot 
    applies a jet veto of $p_\mathrm{T,jet}^\mathrm{veto}=\text{30\,GeV}$. 
    The lower ratio highlights the size of the electroweak corrections.
    \label{fig:aaa:pt}
  }
\end{figure}

Figure \ref{fig:aaa:pt} displays the transverse momenta of the 
first three leading photons. 
The first observation is that, with the chosen set of cuts, 
the leading and subleading photon are of similar hardness, 
and generally much harder than the third leading photon. 
This suggest that we select primarily diphoton production events 
which is accompanied by a third, most bremsstrahlung, photon. 
The NLO QCD corrections exhibit a handful of interesting features. 
In the absence of a jet veto the fixed-order calculation 
exhibits a huge correction factors, mainly induced by the 
opening of new channels in the real emission. 
Similar, kinematic constraints present at LO \footnote{
  At leading order the leading photon needs to be in a different 
  hemisphere than both the subleading and third leading photon. 
  Thus, $\Delta\phi_{\gamma_1\gamma_2}$ and $\Delta\phi_{\gamma_1\gamma_3}$ 
  must be larger that $\tfrac{1}{2}\,\pi$.
} are released and 
lead to a larger phase space that can be populated. 
These findings mandate the inclusion of at least the $\aaa+\text{jet}$ 
production process at NLO QCD to arrive at a reliable description 
of inclusive \aaa\ production, and thus either a NNLO QCD calculation 
or a multijet merging ansatz \cite{Hoeche:2012yf,Kallweit:2015dum}. 
While the inclusive QCD corrections at very small transverse momenta 
are universally large for all three leading photon \pT-spectra 
($\deltaQCD\approx 2$), they remain at exorbitantly large 
($\deltaQCD\approx 1.5$) throughout the considered range 
only for the leading jet \pT. 
For both subleading photons the QCD corrections are quickly 
decreasing, leveling out at a $\approx 20\%$ at large transverse 
momenta.
In the presence of a restrictive jet veto the very low transverse 
momentum region still experiences large correction of about 
$\deltaQCD\approx 1$. 
As transverse momenta are increasing, the QCD corrections now turn 
negative reaching now $-50-60\%$ and for all three photons.

The electroweak corrections, due to the absence of the opening 
of large new channels at the next-to-leading order, are dominated 
by the virtual corrections. 
Consequently, the release of the LO phase space restrictions 
in the real emission corrections only plays a minor role.
For all three photons the electroweak corrections are small but 
positive at small transverse momenta and exhibit the usual 
Sudakov shape at large transverse momenta.
They reach $-10\%$ for the leading and subleading photon and 
$-20\%$ for the third photon at $\pT=500\,\text{GeV}$. 
More importantly, beyond $\pT\gtrsim 170$, 140 and 80\,GeV 
for the first, second and third leading photon, respectively, 
the electroweak corrections are not covered by the LO 
uncertainty estimate.
Due to the different sizes of the QCD and electroweak 
corrections, the additive and multiplicative combination 
of corrections lead to very similar results.

@@

Figure \ref{fig:aaa:myy} continues with the three combinations of 
diphoton invariant masses. 
The \pT\ and $\Delta R$ requirements 
of the event selection induce a minimum in the distributions 
at leading order. 
The region below can only be filled if a fourth particle is 
present, as is the case in both the QCD and electroweak real 
emission corrections, leading to simultaneously huge 
corrections \deltaQCD\ and \deltaEW\ as the Born cross 
section vanishes. 
Due to this behaviour, the multiplicative combination of 
corrections, NLO \QCDtEW, ceases to be well defined and 
spikes in the distribution are visible.
The distributions below, where $\rd\sigma_\text{LO}=0$, 
are ill-defined. 
In consequence, for distributions where kinematic boundaries 
exist at leading order, but are lifted at higher orders, 
the multiplicative combination does not present a viable 
option for describing the observable 
throughout phase space.

The QCD corrections themselves again exceed $200\%$ at 
small invariant masses, already well before the above 
described kinematic boundary effect takes hold. 
As the invariant masses are increasing, the 
QCD corrections are dropping to $20-30\%$ for the inclusive 
selection. 
The structure the QCD corrections exhibit around 80-90\,GeV 
in all three diphoton-pair invariant masses are induced by 
the acceptance cuts.
In the presence of the jet veto, the QCD corrections are 
reduced and turn negative beyond $m_{\gamma\gamma}\gtrsim 300\,\text{GeV}$ 
reaching around $-40\%$ at 1\,TeV. 
The electroweak corrections, on the other hand, are 
again moderate, ranging from $+1.5\%$ between 70 and 200\,GeV 
for $m_{\gamma_1\gamma_2}$ and $m_{\gamma_1\gamma_2}$ and 
0 and 100\,GeV for $m_{\gamma_2\gamma_3}$. 
$m_{\gamma_1\gamma_2}$ exhibits a small rise in the correction 
at $2m_W$ due to resonant box diagrams in that region. 
This feature is also present in the electroweak corrections 
to diphoton production in this observable \cite{Chiesa:2017gqx}. 
At large transverse momentum the usual Sudakov logarithms 
are recoveren, resulting in corrections of around 
$-8\%$ at 1\,TeV for all photon-pair invariant masses. 
Most importantly, beyond $m_{\gamma\gamma}\gtrsim 300\,\text{GeV}$, 
the electroweak corrections are again not covered by the LO 
uncertainty estimate.

@@

@@

Next we move on
